---
title: "Google Scholar webscraping script"
author: "Alberto Agudo Domínguez"
date: '2022-09-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(RSelenium)

# Avoiding scientific notation
options(scipen = 9999)

# Shortcut for CSS selector in Selenium:
css_find <- function(css_selector, one_element = T){
  
  if (one_element) {
    search <- driver$findElement(using = "css", css_selector)
  } else {
    search <- driver$findElements(using = "css", css_selector)
  }
  return(search)
}
```


## 1) Set up Webscraping details
```{r}
rD <- rsDriver(browser = "firefox")
driver <- rD$client

# Check that the browser is navigating properly:
url <- "https://scholar.google.com"
driver$navigate(url)
```


```{r}
# Create a list of all CSS selectors:
css_list <- list()

css_list$search_bar <- "#gs_hdr_tsi"
css_list$button <- "#gs_hdr_tsb"

css_list$first_title <- ".gs_r > .gs_rt a"
css_list$titles <- ".gs_rt a"
css_list$not_first_title <- ".gs_ri .gs_rt a"
css_list$authors_journal_year <- ".gs_a"
css_list$abstracts <- ".gs_rs"
css_list$n_citations <- ".gs_or_btn.gs_nph+ a"

css_list$next_page_button <- "#gs_n > center:nth-child(1) > table:nth-child(1) > tbody:nth-child(1) > tr:nth-child(1) > td:nth-child(12) > a:nth-child(1) > b:nth-child(2)" 
css_list$last_page <- "td:nth-child(11) a"
css_list$final_page_nr <- "#gs_n > center:nth-child(1) > table:nth-child(1) > tbody:nth-child(1) > tr:nth-child(1) > td:nth-child(11) > b:nth-child(2)"

css_list$server_error <- "#gs_top > h1:nth-child(10)"
```



## 2) Set up table to collect the data

```{r}
search_df <- data.frame(title = character(),
                        author_journal = character(),
                        abstract = character(),
                        n_citations = integer())
```


## 3) Webscraping process

*Note: If the name of the topic that the user wants to search also appears as a user profile, this might cause inaccuracies since user profiles appear as another entry (as if Google Scholar was displaying a new paper). To avoid this, our script changes the default search engine language to English and then detects when the first entry is "User Profiles".*

*The script should start running from the URL we provided above (the general Google Scholar search box).*

*Note: The script requires the user to be alert, since sometimes a "Are you a robot" message pops up. Then the search should be stopped and reset at the page where it stopped.*

```{r}
topic <- "intergenerational mobility"

url <- "https://scholar.google.com"
driver$navigate(url)
Sys.sleep(2)

# Search title
search_bar <- css_find(css_list$search_bar)
search_bar$sendKeysToElement(list(topic))

Sys.sleep(1)

button <- css_find(css_list$button)
button$clickElement()

Sys.sleep(2)

# If the user wants to search for a particular time range, they may specify it on
# the advanced search bar of the left and run the script from this point.

# Check that the language is English (it appears in the URL after "hl="XX)
# Otherwise, change language to English
first_page_url <- driver$getCurrentUrl()[[1]]
lang <- str_match(first_page_url, r"{hl=(\w{2,})}")[2]
if (lang != "en"){
  first_page_url <- gsub(r"{hl=(\w{2,})}", r"{hl=en}", first_page_url)
  driver$navigate(first_page_url)
}

# Find last page, click last page, repeat until last page does not change after clicking
# Save number of total pages
# Then come back to the beginning page
last_page_before <- css_find(css_list$last_page)
last_page_before_nr <- as.integer(last_page_before$getElementText()[[1]])
last_page_before$clickElement()

Sys.sleep(2)

last_page_after <- css_find(css_list$last_page)
last_page_after_nr <- as.integer(last_page_after$getElementText()[[1]])

while(last_page_after_nr != last_page_before_nr){
  # Handle the possible error of the final page
  tryCatch(suppressMessages(last_page_before <- css_find(css_list$last_page)),
           error = function(e){last_page_before <<- css_find(css_list$final_page_nr)})
  last_page_before_nr <- as.integer(last_page_before$getElementText()[[1]])
  last_page_before$clickElement()
  
  Sys.sleep(3)
  
  tryCatch(suppressMessages(last_page_after <- css_find(css_list$last_page)),
           error = function(e){last_page_after <<- css_find(css_list$final_page_nr)})
  last_page_after_nr <- as.integer(last_page_after$getElementText()[[1]])
  
  # Handle one type of server error (pages 99 and 100 do not print)
  if ((last_page_after_nr == 100) & (last_page_before_nr == 98)){
    before_click_url <- driver$getCurrentUrl()[[1]]
    
    # Try clicking the new page, if there is a server error determine that
    # the last page to search for is 98
    suppressMessages(last_page_after$clickElement())
    
    # Set as last page the last one before error (and the while loop would finish)
    tryCatch(suppressMessages({server <- css_find(css_list$server_error)
                               last_page_after_nr <- last_page_before_nr},
             error <- function(e){driver$navigate(before_click_url)}))
  }
}

driver$navigate(first_page_url)

Sys.sleep(2)

# Now loop until you finish all pages
for (page_nr in 1:last_page_after_nr){
  
  # Get all titles:
  titles_obj <- css_find(css_list$titles, one_element = F)
  titles <- sapply(titles_obj, function(x) x$getElementText()[[1]])
  
  # Check for User profiles entry in the first page:
  if (page_nr == 1){
  
  profiles <- sapply(titles, function(x) startsWith(x, "User profiles"))
  
  if (sum(profiles) > 0){
    location <- which(profiles)
    titles <- titles[-location]
    }
  }
  
  # All authors + journal + year of publication:
  author_journal_obj <- css_find(css_list$authors_journal_year, one_element = F)
  author_journal <- sapply(author_journal_obj, function(x) x$getElementText()[[1]])

  # Abstract:
  abstracts_obj <- css_find(css_list$abstracts, one_element = F)
  abstracts <- sapply(abstracts_obj, function(x) x$getElementText()[[1]])
  
  # Citations:
  citations_obj <- css_find(css_list$n_citations, one_element = F)
  n_citations <- sapply(citations_obj, function(x) {text <- x$getElementText()[[1]]
                                                    return(str_match(text,
                                                                     r"{Cited by ([0-9]+)}")[2])})
  
  # Create a DataFrame with all information from this page and append it to our
  # original DF
  page_info <- cbind(titles, author_journal, abstracts, n_citations)
  
  search_df <- rbind(search_df, page_info)
  
  
  # Click next page button:
  try(suppressMessages({next_page_button <- css_find(css_list$next_page_button)
      next_page_button$clickElement()}),
      silent = T)
  
  print(paste("Completed page", page_nr, "/", last_page_after_nr))
  
  Sys.sleep(2)
}


```


```{r}
# Check for duplicates:
sum(duplicated(search_df))

# Get cleaner info on authors, journal of publication, year of publication
# and webpage.
author_journalyear_page <- str_split(search_df$author_journal, " - ")

get_year <- function(vector){
  journal_year <- sapply(vector, function(x) x[2])
  years <- sapply(journal_year, function(x) as.integer(str_match(x, "(, )?([0-9]+)")[3]))
  return(years)
}

get_journal <- function(vector){
  journal_year <- sapply(vector, function(x) x[2])
  journal <- sapply(journal_year, function(x) gsub("(, )?([0-9]+)", "", x))
  return(journal)
  
}

search_df$author <- sapply(author_journalyear_page, function(x) x[1])
search_df$journal <- get_journal(author_journalyear_page)
search_df$year <- get_year(author_journalyear_page)
search_df$page <- sapply(author_journalyear_page, function(x) x[3])

search_df
```



## 4) Save

```{r}
write_csv(search_df, "../data/search_df.csv")
```


```{r}
# Close the driver:
driver$close()
rD$server$stop()
```

